BarnebyLives':' an R package to create herbarium specimen labels and digital data sheets

### 2023-11-20 manuscript/manuscript_APPS.rmd
going to transition local taxonomic look up source to kews! redo parsing for better spell check

Recent innovations in computing, specimen digitization, data sharing, DNA sequencing, and statistics have brought about a renaissance in herbarium based studies (@greve2016realising, @james2018herbarium, @brewer2019factors, @ronsted2020integrative). 
Current uses of specimen based data extend far beyond their traditional roles in systematics and floristics, and studies utilizing collections are regularly carried out to better understand the ecological niches, phenological processes, and interactions of plants (@ronsted2020integrative). 
However, we anticipate that collections will gain their most widespread utilization as natural history is being revitalized in ecology, via novel approaches, such as remote sensing, meta-barcoding, community science, electronic sensing (@tosa2021rapid).

@@

@@

 pow_res <- lapply(names,
       powo_searcher) %>% 
       bind_rows()
 data <- bind_cols(data, pow_res)

@@

@@

epithet_diff <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(Epithet != POW_Epithet, !Full_name %in% 
           unique(c( genera_mispelled$Full_name,  genus_mismatch$Full_name))) %>% 
  select(Collection_number, Full_name, Epithet, POW_Genus, POW_Epithet, POW_Infraspecies) %>% 
  distinct(Full_name, .keep_all = T) %>%  # do we record repeat collections ?
  mutate(Situation = 
           case_when(
             Collection_number %in% c('1217') ~ 'Spelling',
             Collection_number %in% c('1588', '2445', '2777', '1337', '2412', '2748', 
                                      '2652', '2805', '2194', '2040', '2039', '2403', '2328') ~ 'Outdated',
             Collection_number %in% c('2326', '2038') ~ 'Internal_Error' ,
             Collection_number %in% c('2110') ~ 'Preferred'

@@

srm(Family_in, Family_out)
```

>>>>

Recent innovations in computing, specimen digitization, data sharing, DNA sequencing, and statistics have brought about a renaissance in herbarium based studies (@greve2016realising, @james2018herbarium, @brewer2019factors, @ronsted2020integrative). 
Current uses of specimen based data extend far beyond their traditional roles in systematics and floristics, and studies utilizing collections are regularly carried out to better understand the ecological niches, phenological processes, and interactions of plants (@ronsted2020integrative). 
Even within systematics, the ability to collect and analyze micro-morphological data has fostered revisionary studies in many groups providing synapomorphies which can be correlated to molecular results to improve the interpretation of monophyletic clades. 
However, we anticipate that collections will gain their most widespread utilization as natural history is being revitalized in ecology, via novel approaches, such as remote sensing, meta-barcoding, community science, and electronic sensing (@tosa2021rapid).

@@

filter(sct, Match == 'fuzzy') %>% 
  select(Scientific_name, 'SpellCk.scientificName')

@@

 pow_res1 <- lapply(names[1],
       powo_searcher) %>% 
       bind_rows()
 data <- bind_cols(data, pow_res)

@@

names

@@

epithet_diff <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(Epithet != POW_Epithet, !Full_name %in% 
           unique(c( genera_mispelled$Full_name,  genus_mismatch$Full_name))) %>% 
  select(Collection_number, Full_name, Epithet, POW_Genus, POW_Epithet, POW_Infraspecies) %>% 
  distinct(Full_name, .keep_all = T) %>%  # do we record repeat collections ?
  mutate(Situation = 
           case_when(
             Collection_number %in% c('1217') ~ 'Spelling',
             Collection_number %in% c('1588', '2445', '2777', '1337', '2412', '2748', 
                                      '2652', '2805', '2194', '2040', '2039', '2403',
                                      '2328', '2076') ~ 'Outdated',
             Collection_number %in% c('2326', '2038', '1424', '2618', '2665', '2297') ~ 'Internal_Error',
             Collection_number %in% c('2110') ~ 'Preferred'

@@

rm(Family_in, Family_out)
```
